---
title: "NATSAP: T-test for Youth OQ Admission vs. Discharge"
output: html_document
---

## Preliminaries

Load libraries: `rstan` for using STAN for Bayesian sampling and `foreign` for importing an SPSS file.

```{r, message=FALSE}
library(rstan)
library(foreign)
```

The `plotpost` function gives us pretty graphics for Bayesian inference. We should look into using `mcmcplots` or `ggmcmc` instead.

```{r}
source("plotPost.R")
```

## Import Data

The `memisc` package stopped working for me, but `foreign` does a nice job withthe exception of throwing a few warnings that I'm not sure about.

```{r}
NATSAP <- read.spss("NATSAP_PRN_DATABASE.sav", to.data.frame = TRUE)
```


## Prepare data

The `whichDiff` function is a simple way to grab the difference of any two variables.

```{r}
whichDiff <- function(x1, x2){
  NATSAP[x1] - NATSAP[x2]
}
```

For convenience, we use abbreviated variable names.

```{r}
YAdd <- "YOUTHOQAdmissionTotalScore"
YDis <- "YOUTHOQDischargeTotalScore"
```

For this test, we're interested in the difference between youth OQ scores at admission and discharge.


```{r}
diff <- whichDiff(YAdd, YDis)
diff <- diff[!is.na(diff)]
nSubj <- length(diff)
```

## Stan

Stan requires data to be passed as a list.

```{r}
dataList <- list( 
  nSubj = nSubj ,
  diff = diff)
```

Here we define the Stan model code.

```{r}
model = "
data {
    int<lower=0> nSubj; //number of subjects
    real diff[nSubj];   //treatment effect
}
parameters {
    real mu; 
    real<lower=0> sigma;
}
model {
    diff ~ normal(mu, sigma);
}
"
```

Fit the Stan model.

```{r, cache=TRUE}
fit <- stan(model_code = model, data = dataList)
```

Extract the samples, view the summary statistics for the parameters, and check the convergence and mixing of the chains.

```{r}
samplesSet = extract(fit, pars =  c("mu"))
print(fit, digits_summary = 3)
traceplot(fit, pars = c("mu"))
```

The parameter of interest is `mu`.

```{r}
mu = t(samplesSet$mu)
chainLength = NCOL(mu)
```

## Inference

Here we produce a histogram and credible interval for `mu`.

```{r}
source("plotPost.R")
plotPost( mu , xlab=expression(mu[diff]) , main="" ,
          breaks=20)
```

## T-test

We run a t-test to compare our Bayesian inference to the classical test.

```{r}
print(t.test(diff))
```