---
title: "Youth OQ T-test"
output: html_document
---

Here we run a simple t-test on the difference between Youth OQ scores at admission and discharge. First we run basic (non-hierarchical) Bayes, and then follow up with a classical t-test. Both methods yield nearly identical results.

## Preliminaries

Load libraries: `rstan` for using STAN for Bayesian sampling and `foreign` for importing an SPSS file.

```{r, message=FALSE}
library(rstan)
library(foreign)
```

The `plotpost` function from Kruschke allows us to make pretty graphs. We should look into using `ggplot2`, maybe even through the `ggmcmc` package or something similar.

```{r}
source("plotPost.R")
```

## Importing and cleaning data

Import the data and subset for OQ scores.

```{r cache=TRUE}
NATSAP <- read.spss("NewNATSAP.sav")
NATSAP <- as.data.frame(NATSAP)
```

(The `foreign` package seems to work more smoothly than `memisc`, but it's generating a few weird errors I should look into.)

## Extracting the data of interest

The `whichDiff` function will produce vectors of differences between two columns.

```{r}
whichDiff <- function(x1, x2){
  NATSAP[x1] - NATSAP[x2]
}
```

Get the variables we want to compare.

```{r}
YAdd <- "AdmissionTotalScore"
YDis <- "DischargeTotalScore"
diff <- whichDiff(YAdd, YDis)
diff <- diff[!is.na(diff)]
nSubj <- length(diff)
```

## The STAN model

We specify the model in STAN code.

```{r}
stan_model <- "
//This is the stan model for non-hierarchical t-test
data {
    int<lower=0> nSubj; //number of subjects
    real diff[nSubj];   //treatment effect
}
parameters {
    real mu; 
    real<lower=0> sigma;
}
model {
    diff ~ normal(mu, sigma);
}"
```

STAN requires us to pass all the data in a list.

```{r}
dataList <- list( 
  nSubj = nSubj ,
  diff = diff)
```

Now fit the model in STAN.

```{r, cache=TRUE, message=FALSE, warning=FALSE}
fit <- stan(model_code = stan_model, data = dataList, verbose = FALSE)
```

[No amount of setting flags equal to FALSE seems to get rid of all this annoying STAN output.]

## Conclusions

We extract the samples and examine them for convergence.

```{r}
samplesSet = extract(fit, pars =  c("mu"))
print(fit, digits_summary = 3)
traceplot(fit, pars = c("mu"))
```

Extract the parameters we want to analyze.

```{r}
mu = t(samplesSet$mu)
chainLength = NCOL(mu)
```

Now we create a histogram with HDI of the mean difference between youth intake and youth discharge scores.

```{r}
layout( matrix(1:1,nrow=1) ) #This was originally matrix(1:3)
plotPost( mu , xlab=expression(mu[diff]) , main="" ,
          breaks=20)
```

By way of contrast, here is a simple t-test to compare the Bayesian version to the classical version.

```{r}
print(t.test(diff))
```