---
title: "Building up models for NATSAP data"
author: "Sean Raleigh"
date: "Tuesday, January 27, 2015"
output: html_document
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(cache=TRUE)
```

## Introduction

In this document, we build up models for the NATSAP data, starting from very simple models and gradually getting more and more complex.

## Read in data

Code to read and clean the data.

```{r, comment=FALSE, message=FALSE, warning=FALSE}
library(lme4)
library(rstan)
library(dplyr)
library(tidyr)
library(ggplot2)

## Import Data
natsap <- read.csv("NewNATSAP.csv")
dose <- read.csv("NATSAPDoseData.csv")

## Get rid of program with no NatsapID
dose <- dose[!is.na(dose$NatsapId),]

## Select only wanted variables and create diff
natsap_tidy <- natsap %>%
    select(ID = NatsapId,
           sex = GenderNumeric, 
           admission_OQ = AdmissionTotalScore,
           discharge_OQ = DischargeTotalScore) %>%
    mutate(diff = admission_OQ - discharge_OQ)

        
natsap_tidy <- natsap_tidy[complete.cases(natsap_tidy),]

dose_tidy <- dose %>%
    transmute(RTC_OBH = RTCvsOBH,
           ID = NatsapId,
           IT = Mode.minutes.of.Inidividual.Therapy,
           mean_IT = mean(Mode.minutes.of.Inidividual.Therapy),
           IT_cent = IT - mean_IT,
           GT = Mode.minutes.of.Group.Therapy,
           mean_GT = mean(Mode.minutes.of.Group.Therapy),
           GT_cent = GT - mean_GT,
           RFT = Mode.minutes..of.Remote.Family.Therapy.per.week,
           mean_RFT = mean(Mode.minutes..of.Remote.Family.Therapy.per.week),
           RFT_cent = RFT - mean_RFT)

## Creates new program IDs incrementing from 1 for loops in Stan
## lookup is the intersection of ID from dose_tidy and natsap_tidy
natsap_tidy_ID <- select(natsap_tidy, ID)
dose_tidy_ID <- select(dose_tidy, ID)
lookup <- semi_join(dose_tidy_ID, natsap_tidy_ID)
lookup <- cbind(lookup, new_ID = 1:length(lookup$ID))

## Selects only the cases in the dataframes that have IDs in Lookup
## and adds a column including the new indices for the NatsapIds
natsap_tidy <- natsap_tidy %>%
    inner_join(lookup, by = "ID") %>%
    arrange(new_ID)
dose_tidy <- dose_tidy %>%
    inner_join(lookup, by = "ID") %>%
    arrange(new_ID)

## Add sample sizes for each program
n_by_program <- natsap_tidy %>%
    group_by(new_ID) %>%
    summarize(n = n())

dose_tidy <- cbind(dose_tidy, n = n_by_program$n)

## Make factor variable and relevel

natsap_tidy <- natsap_tidy %>%
    mutate(new_ID = as.factor(new_ID),
           sex = as.factor(sex))

## Recode 0/1 as "male" and "female"
levels(natsap_tidy$sex)[levels(natsap_tidy$sex) == 0] <- "Male"
levels(natsap_tidy$sex)[levels(natsap_tidy$sex) == 1] <- "Female"

## Defines Variables to be passed to Stan
## IPred and GPred have a column of 1's representing the constant term
n_subj <- nrow(natsap_tidy)
n_prog <- nrow(dose_tidy)
sex <- select(natsap_tidy, sex)
ind_pred <- cbind(rep(1, n_subj), sex)
IT <- select(dose_tidy, IT)
IT_cent <- select(dose_tidy, IT_cent)
GT <- select(dose_tidy, GT)
GT_cent <- select(dose_tidy, GT_cent)
RFT <- select(dose_tidy, RFT)
RFT_cent <- select(dose_tidy, RFT_cent)
RTC_OBH <- select(dose_tidy, RTC_OBH)
group_pred <- cbind(rep(1, n_prog), IT_cent, GT_cent, RFT_cent, RTC_OBH)
diff <- natsap_tidy$diff
ID = select(natsap_tidy, ID)


## Put data in a list for Stan
data_list <- list(n_subj = n_subj,
                  n_prog = n_prog,
                  n_ind_pred = ncol(ind_pred),
                  n_group_pred = ncol(group_pred),
                  diff = diff,
                  ID = ID,
                  ind_pred = ind_pred,
                  group_pred = group_pred)

## Wihtout having to load the arm package, we can still use the handy
## functions se.fixef and se.ranef
se.fixef <- function (object) 
{
    fcoef.name <- names(fixef(object))
    corF <- vcov(object)@factors$correlation
    ses <- corF@sd
    names(ses) <- fcoef.name
    return(ses)
}

se.ranef <- function (object) 
{
    se.bygroup <- ranef(object, condVar = TRUE)
    n.groupings <- length(se.bygroup)
    for (m in 1:n.groupings) {
        vars.m <- attr(se.bygroup[[m]], "postVar")
        K <- dim(vars.m)[1]
        J <- dim(vars.m)[3]
        names.full <- dimnames(se.bygroup[[m]])
        se.bygroup[[m]] <- array(NA, c(J, K))
        for (j in 1:J) {
            se.bygroup[[m]][j, ] <- sqrt(diag(as.matrix(vars.m[, 
                , j])))
        }
        dimnames(se.bygroup[[m]]) <- list(names.full[[1]], names.full[[2]])
    }
    return(se.bygroup)
}
```

## Simple linear models

First, let's only consider group differences.

```{r}
fit_simple1 <- lm(diff ~ 1, data = natsap_tidy)
fit_simple2 <- lm(diff ~ new_ID - 1, data = natsap_tidy)
fit_simple3 <- lmer(diff ~ (1|new_ID), data = natsap_tidy)

## Extract coeffiencts and st errors
int_simple1 <- summary(fit_simple1)$coef[,1]
int_simple2 <- data.frame(int_simple = summary(fit_simple2)$coef[,1])
se_int_simple2 <- data.frame(se_int_simple = summary(fit_simple2)$coef[,2])
int_simple3 <-
    data.frame(int_simple =
               unname(fixef(fit_simple3)) + ranef(fit_simple3)$new_ID[,1])
se_int_simple3 <- 
    data.frame(se_int_simple =
               se.ranef(fit_simple3)$new_ID[,1])
int_simple_a <- 
    cbind(new_ID = as.factor(dose_tidy$new_ID),
          model = rep("Unpooled", length(int_simple2)),      
          int_simple = int_simple2,
          se_int_simple = se_int_simple2)
rownames(int_simple_a) <- NULL
int_simple_b <- 
    cbind(new_ID = as.factor(dose_tidy$new_ID),
          model = rep("Partially pooled", length(int_simple3)),
          int_simple = int_simple3,
          se_int_simple = se_int_simple3)
int_simple <- rbind(int_simple_a, int_simple_b)
limits_simple <- aes(ymax = int_simple + se_int_simple,
    ymin = int_simple - se_int_simple)
ggplot(int_simple, aes(x = new_ID, y = int_simple, color = model)) +
    geom_pointrange(limits_simple, position = position_dodge(width = 0.2)) +
    geom_hline(yintercept = fixef(fit_simple3))

```


Let's look only at `diff` by `sex`. This is what Gelman and Hill call "complete pooling".

```{r}
fit_pooled <- lm(diff ~ sex - 1, data = natsap_tidy)
summary(fit_pooled)
```

Contrast this with no pooling.

```{r}
fit_unpooled <- lm(diff ~ sex + new_ID - 1, data = natsap_tidy)
summary(fit_unpooled)
```

We use `lmer` from the `lme4` package to create a varying intercept model.

```{r}
fit_vint <- lmer(diff ~ sex + (1 | new_ID), data = natsap_tidy)
summary(fit_vint)
coef(fit_vint)
fixef(fit_vint)
ranef(fit_vint)
```

## Hierarchical models

Now we add a group-level predictor.
```{r}
## We need to grab the minutes of individual and group therapy for each individual
## as well as the value of RTC_OBH
IT_full <- IT_cent[natsap_tidy$new_ID,]
GT_full <- GT_cent[natsap_tidy$new_ID,]
RFT_full <- RFT_cent[natsap_tidy$new_ID,]
RTC_OBH_full <- RTC_OBH[natsap_tidy$new_ID,]


## The model for individual therapy
fit_hier_vint_IT <- lmer(diff ~ sex + IT_full + (1 | new_ID),
    data = natsap_tidy)
summary(fit_hier_vint_IT)
coef(fit_hier_vint_IT)
fixef(fit_hier_vint_IT)
ranef(fit_hier_vint_IT)

## The model for group therapy
fit_hier_vint_GT <- lmer(diff ~ sex + GT_full + (1 | new_ID),
    data = natsap_tidy)
summary(fit_hier_vint_GT)
coef(fit_hier_vint_GT)
fixef(fit_hier_vint_GT)
ranef(fit_hier_vint_GT)

## The model for remote family therapy
fit_hier_vint_RFT <- lmer(diff ~ sex + RFT_full + (1 | new_ID),
    data = natsap_tidy)
summary(fit_hier_vint_RFT)
coef(fit_hier_vint_RFT)
fixef(fit_hier_vint_RFT)
ranef(fit_hier_vint_RFT)

## The model for RTC_OBH
fit_hier_vint_RTC_OBH <-
    lmer(diff ~ sex + RTC_OBH_full + (1 | new_ID),
    data = natsap_tidy)
summary(fit_hier_vint_RTC_OBH)
coef(fit_hier_vint_RTC_OBH)
fixef(fit_hier_vint_RTC_OBH)
ranef(fit_hier_vint_RTC_OBH)
```

We realize that we need to control not only for `sex`, but also for `RTC_OBH`. There appears to be a bigger difference for females in RTC programs (because of the much higher admission scores).

```{r}
## The model for individual therapy
fit_hier_vint_IT2 <- lmer(diff ~ sex + RTC_OBH_full + IT_full + (1 | new_ID),
    data = natsap_tidy)
summary(fit_hier_vint_IT2)
coef(fit_hier_vint_IT2)
fixef(fit_hier_vint_IT2)
ranef(fit_hier_vint_IT2)

## The model for group therapy
fit_hier_vint_GT2 <- lmer(diff ~ sex + RTC_OBH_full + GT_full + (1 | new_ID),
    data = natsap_tidy)
summary(fit_hier_vint_GT2)
coef(fit_hier_vint_GT2)
fixef(fit_hier_vint_GT2)
ranef(fit_hier_vint_GT2)

## The model for remote family therapy
fit_hier_vint_RFT2 <- lmer(diff ~ sex + RTC_OBH_full + RFT_full + (1 | new_ID),
    data = natsap_tidy)
summary(fit_hier_vint_RFT2)
coef(fit_hier_vint_RFT2)
fixef(fit_hier_vint_RFT2)
ranef(fit_hier_vint_RFT2)
```


Let's try to plot something.
```{r}

## Extract coefficients for minutes of individual therapy
int_IT <-coef(fit_hier_vint_IT)$new_ID[,1]
se_int_IT <- se.ranef(fit_hier_vint_IT)$new_ID[,1]
int_by_IT <- 
    data.frame(dose_tidy$new_ID, IT, int_IT, se_int_IT)
limits_ind <- aes(ymax = int_IT + se_int_IT, ymin = int_IT - se_int_IT)
ggplot(int_by_IT, aes(x = IT, y = int_IT)) +
    geom_pointrange(limits_ind, position = position_jitter(width = 1))

## Extract coefficients for minutes of group therapy
int_GT <-coef(fit_hier_vint_GT)$new_ID[,1]
se_int_GT <- se.ranef(fit_hier_vint_GT)$new_ID[,1]
int_by_GT <- 
    data.frame(dose_tidy$new_ID, GT,int_GT, se_int_GT)
limits_group <- aes(ymax = int_GT + se_int_GT, ymin = int_GT - se_int_GT)
ggplot(int_by_GT, aes(x = GT, y = int_GT)) +
    geom_pointrange(limits_group, position = position_jitter(width = 2))

## Extract coefficients for minutes of remote family therapy
int_RFT <-coef(fit_hier_vint_RFT)$new_ID[,1]
se_int_RFT <- se.ranef(fit_hier_vint_RFT)$new_ID[,1]
int_by_RFT <- 
    data.frame(dose_tidy$new_ID, RFT,int_RFT, se_int_RFT)
limits_RFT <- aes(ymax = int_RFT + se_int_RFT, ymin = int_RFT - se_int_RFT)
ggplot(int_by_RFT, aes(x = RFT, y = int_RFT)) +
    geom_pointrange(limits_RFT, position = position_jitter(width = 2))

## Extract coefficients for RTC_OBH
int_RTC_OBH <-coef(fit_hier_vint_RTC_OBH)$new_ID[,1]
se_int_RTC_OBH <- se.ranef(fit_hier_vint_RTC_OBH)$new_ID[,1]
int_by_RTC_OBH <- 
    data.frame(dose_tidy$new_ID, RTC_OBH,int_RTC_OBH, se_int_RTC_OBH)
limits_RTC_OBH <- aes(ymax = int_RTC_OBH + se_int_RTC_OBH,
    ymin = int_RTC_OBH - se_int_RTC_OBH)
ggplot(int_by_RTC_OBH, aes(x = RTC_OBH, y = int_RTC_OBH)) +
    geom_pointrange(limits_RTC_OBH, position = position_jitter(width = 0.1))
```

Repeat for the models controling for both `sex` and `RTC_OBH`.

```{r}

## Extract coefficients for minutes of individual therapy
int_IT2 <-coef(fit_hier_vint_IT2)$new_ID[,1]
se_int_IT2 <- se.ranef(fit_hier_vint_IT2)$new_ID[,1]
int_by_IT2 <- 
    data.frame(dose_tidy$new_ID, IT, int_IT2, se_int_IT2)
limits_ind2 <- aes(ymax = int_IT2 + se_int_IT2, ymin = int_IT2 - se_int_IT2)
plot_IT2 <- ggplot(int_by_IT2, aes(x = IT, y = int_IT2)) +
    geom_pointrange(limits_ind2, position = position_jitter(width = 2))
plot_IT2

## Extract coefficients for minutes of group therapy
int_GT2 <-coef(fit_hier_vint_GT2)$new_ID[,1]
se_int_GT2 <- se.ranef(fit_hier_vint_GT2)$new_ID[,1]
int_by_GT2 <- 
    data.frame(dose_tidy$new_ID, GT,int_GT2, se_int_GT2)
limits_group2 <- aes(ymax = int_GT2 + se_int_GT2, ymin = int_GT2 - se_int_GT2)
plot_GT2 <- ggplot(int_by_GT2, aes(x = GT, y = int_GT2)) +
    geom_pointrange(limits_group2, position = position_jitter(width = 8))
plot_GT2

## Extract coefficients for minutes of remote family therapy
int_RFT2 <-coef(fit_hier_vint_RFT2)$new_ID[,1]
se_int_RFT2 <- se.ranef(fit_hier_vint_RFT2)$new_ID[,1]
int_by_RFT2 <- 
    data.frame(dose_tidy$new_ID, RFT,int_RFT2, se_int_RFT2)
limits_RFT2 <- aes(ymax = int_RFT2 + se_int_RFT2, ymin = int_RFT2 - se_int_RFT2)
plot_RFT2 <- ggplot(int_by_RFT2, aes(x = RFT, y = int_RFT2)) +
    geom_pointrange(limits_RFT2, position = position_jitter(width = 4))
plot_RFT2
```

What if we didn't look at `diff`? Since all outcomes seem to be roughly the same, what if we only look at `discharge_OQ`?

```{r}
## The model for individual therapy
fit_hier_vint_IT3 <- lmer(discharge_OQ ~ sex + RTC_OBH_full + IT_full + (1 | new_ID),
    data = natsap_tidy)
summary(fit_hier_vint_IT3)
coef(fit_hier_vint_IT3)
fixef(fit_hier_vint_IT3)
ranef(fit_hier_vint_IT3)

## The model for group therapy
fit_hier_vint_GT3 <- lmer(discharge_OQ ~ sex + RTC_OBH_full + GT_full + (1 | new_ID),
    data = natsap_tidy)
summary(fit_hier_vint_GT3)
coef(fit_hier_vint_GT3)
fixef(fit_hier_vint_GT3)
ranef(fit_hier_vint_GT3)

## The model for remote family therapy
fit_hier_vint_RFT3 <- lmer(discharge_OQ ~ sex + RTC_OBH_full + RFT_full + (1 | new_ID),
    data = natsap_tidy)
summary(fit_hier_vint_RFT3)
coef(fit_hier_vint_RFT3)
fixef(fit_hier_vint_RFT3)
ranef(fit_hier_vint_RFT3)

## Extract coefficients for minutes of individual therapy
int_IT3 <-coef(fit_hier_vint_IT3)$new_ID[,1]
se_int_IT3 <- se.ranef(fit_hier_vint_IT3)$new_ID[,1]
int_by_IT3 <- 
    data.frame(dose_tidy$new_ID, IT, int_IT3, se_int_IT3)
limits_ind3 <- aes(ymax = int_IT3 + se_int_IT3, ymin = int_IT3 - se_int_IT3)
ggplot(int_by_IT3, aes(x = IT, y = int_IT3)) +
    geom_pointrange(limits_ind3, position = position_jitter(width = 1))

## Extract coefficients for minutes of group therapy
int_GT3 <-coef(fit_hier_vint_GT3)$new_ID[,1]
se_int_GT3 <- se.ranef(fit_hier_vint_GT3)$new_ID[,1]
int_by_GT3 <- 
    data.frame(dose_tidy$new_ID, GT,int_GT3, se_int_GT3)
limits_group3 <- aes(ymax = int_GT3 + se_int_GT3, ymin = int_GT3 - se_int_GT3)
ggplot(int_by_GT3, aes(x = GT, y = int_GT3)) +
    geom_pointrange(limits_group3, position = position_jitter(width = 2))

## Extract coefficients for minutes of remote family therapy
int_RFT3 <-coef(fit_hier_vint_RFT3)$new_ID[,1]
se_int_RFT3 <- se.ranef(fit_hier_vint_RFT3)$new_ID[,1]
int_by_RFT3 <- 
    data.frame(dose_tidy$new_ID, RFT,int_RFT3, se_int_RFT3)
limits_RFT3 <- aes(ymax = int_RFT3 + se_int_RFT3, ymin = int_RFT3 - se_int_RFT3)
ggplot(int_by_RFT3, aes(x = RFT, y = int_RFT3)) +
    geom_pointrange(limits_RFT3, position = position_jitter(width = 2))
```

# Descriptive Statistics

## Sample sizes

```{r}
## Sample size check
sample_check <- data.frame(new_ID = dose_tidy$new_ID, n = dose_tidy$n,
                           RTC_OBH,int_RTC_OBH, se_int_RTC_OBH)
sample_check <- sample_check %>%
    arrange(RTC_OBH, new_ID)
sample_check

sample_check_totals <- sample_check %>%
    group_by(RTC_OBH) %>%
    summarise(sum(n))
sample_check_totals

sample_by_sex <- natsap_tidy %>%
    group_by(new_ID, sex) %>%
    summarise(n = n())
prog_type <- RTC_OBH[sample_by_sex$new_ID,]
sample_by_sex <- sample_by_sex %>%
    cbind(prog_type) %>%
    arrange(prog_type, new_ID)
sample_by_sex

sample_by_sex_totals <- sample_by_sex %>%
    group_by(prog_type, sex) %>%
    summarise(sum(n))
sample_by_sex_totals


```


## RTC_vs_OBH OQ

```{r}
OQ <- cbind(natsap_tidy, RTC_OBH_full)
OQ_summary <- OQ %>%
    group_by(RTC_OBH_full, sex) %>%
    summarize(median(admission_OQ), median(discharge_OQ), median(diff))
OQ_summary

OQ_adm_dis <- OQ %>%
    gather(adm_dis, OQ, admission_OQ, discharge_OQ)
levels(OQ_adm_dis$adm_dis)[levels(OQ_adm_dis$adm_dis) == "admission_OQ"] <- 
    "Admission OQ"
levels(OQ_adm_dis$adm_dis)[levels(OQ_adm_dis$adm_dis) == "discharge_OQ"] <- 
    "Discharge OQ"

plot_OQ_adm_dis <- ggplot(OQ_adm_dis, aes(x = RTC_OBH_full,
               y = OQ,
               fill = sex)) +
    geom_boxplot() +
    facet_grid(. ~ adm_dis) +
    xlab("") +
    scale_fill_discrete(name="Sex") +
    theme(strip.text.x = element_text(size=16))
plot_OQ_adm_dis

plot_OQ_diff <- ggplot(OQ, aes(x = RTC_OBH_full, y = diff, fill = sex)) +
    geom_boxplot() +
    xlab("") +
    ylab("OQ difference") +
    scale_fill_discrete(name="Sex") +
    theme(axis.title.y = element_text(size=16))
plot_OQ_diff
```

That was for only `natsap_tidy`. Does this look different for the whole NATSAP database?


```{r}
OQ2 <- natsap %>%
    select(ID = NatsapId,
           sex = GenderNumeric, 
           admission_OQ = AdmissionTotalScore,
           discharge_OQ = DischargeTotalScore,
           RTC_OBH = RTCvsOBH) %>%
    mutate(diff = admission_OQ - discharge_OQ)

        
OQ2 <- OQ2[complete.cases(OQ2),]

## Make factor variable and relevel

OQ2 <- OQ2 %>%
    mutate(sex = as.factor(sex))

## Recode 0/1 as "male" and "female"
levels(OQ2$sex)[levels(OQ2$sex) == 0] <- "Male"
levels(OQ2$sex)[levels(OQ2$sex) == 1] <- "Female"


OQ_summary2 <- OQ2 %>%
    group_by(RTC_OBH, sex) %>%
    summarize(median(admission_OQ), median(discharge_OQ), median(diff))
OQ_summary2

OQ_adm_dis2 <- OQ2 %>%
    gather(adm_dis, OQ, admission_OQ, discharge_OQ)
levels(OQ_adm_dis2$adm_dis)[levels(OQ_adm_dis2$adm_dis) == "admission_OQ"] <- 
    "Admission OQ"
levels(OQ_adm_dis2$adm_dis)[levels(OQ_adm_dis2$adm_dis) == "discharge_OQ"] <- 
    "Discharge OQ"

ggplot(OQ_adm_dis2, aes(x = RTC_OBH,
               y = OQ,
               fill = sex)) +
    geom_boxplot() +
    facet_grid(. ~ adm_dis) +
    xlab("") +
    scale_fill_discrete(name="Sex") +
    theme(strip.text.x = element_text(size=16))

ggplot(OQ2, aes(x = RTC_OBH, y = diff, fill = sex)) +
    geom_boxplot() +
    xlab("") +
    ylab("OQ difference") +
    scale_fill_discrete(name="Sex") +
    theme(axis.title.y = element_text(size=16))
```

## Dose data

```{r}
dose_tidy %>%
    select(RTC_OBH, IT, GT, RFT) %>%
    arrange(RTC_OBH, IT, GT, RFT)
```

## Clean up plots for presentation

```{r}
plot_IT2 <- plot_IT2 +
    xlab("Minutes of Individual Therapy") +
    ylab("OQ difference") +
    theme(axis.title.x = element_text(size=32),
          axis.text.x  = element_text(size=16)) +
    theme(axis.title.y = element_text(size=32),
          axis.text.y  = element_text(size=16)) +
    scale_x_continuous(breaks = seq(60, 120, 30), minor_breaks = NULL)
plot_IT2

plot_GT2 <- plot_GT2 +
    xlab("Minutes of Group Therapy") +
    ylab("OQ difference") +
    theme(axis.title.x = element_text(size=32),
          axis.text.x  = element_text(size=16)) +
    theme(axis.title.y = element_text(size=32),
          axis.text.y  = element_text(size=16))
plot_GT2

plot_RFT2 <- plot_RFT2 +
    xlab("Minutes of Family Therapy") +
    ylab("OQ difference") +
    theme(axis.title.x = element_text(size=32),
          axis.text.x  = element_text(size=16)) +
    theme(axis.title.y = element_text(size=32),
          axis.text.y  = element_text(size=16))
plot_RFT2

plot_OQ_adm_dis <- ggplot(OQ_adm_dis, aes(x = RTC_OBH_full,
               y = OQ,
               fill = sex)) +
    geom_boxplot() +
    facet_grid(. ~ adm_dis) +
    xlab("") +
    scale_fill_discrete(name="Sex") +
    theme(strip.text.x = element_text(size=16),
          axis.text.x = element_text(size=16)) +
    theme(axis.title.y = element_text(size=32),
          axis.text.y  = element_text(size=16)) +
    theme(legend.title = element_text(size=16),
          legend.text = element_text(size=16))
plot_OQ_adm_dis

plot_OQ_diff <- ggplot(OQ, aes(x = RTC_OBH_full, y = diff, fill = sex)) +
    geom_boxplot() +
    xlab("") +
    ylab("OQ difference") +
    scale_fill_discrete(name="Sex") +
    theme(axis.text.x = element_text(size=16)) +
    theme(axis.title.y = element_text(size=32),
          axis.text.y = element_text(size=16)) +
    theme(legend.title = element_text(size=16),
          legend.text = element_text(size=16))
plot_OQ_diff
```
